%% CV – Njome David (English version)
%% Compiler : xelatex or pdflatex
\documentclass[10pt, a4paper]{article}

% ── Packages ────────────────────────────────────────────────────────────────
\usepackage[a4paper, top=1.2cm, bottom=1.2cm, left=1.4cm, right=1.4cm]{geometry}
\usepackage{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{array}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{multirow}
\usepackage{booktabs}

% ── Colors ──────────────────────────────────────────────────────────────────
\definecolor{navyblue}{HTML}{1F4E79}
\definecolor{darkgray}{HTML}{595959}
\definecolor{lightgray}{HTML}{F2F2F2}

% ── Hyperlinks ───────────────────────────────────────────────────────────────
\hypersetup{
  colorlinks=true,
  urlcolor=navyblue,
  linkcolor=navyblue
}

% ── No page number ───────────────────────────────────────────────────────────
\pagestyle{empty}

% ── Section style ────────────────────────────────────────────────────────────
\titleformat{\section}
  {\large\bfseries\color{navyblue}}
  {}{0em}
  {}
  [\vspace{-6pt}\textcolor{navyblue}{\rule{\linewidth}{1.2pt}}\vspace{2pt}]

\titlespacing{\section}{0pt}{10pt}{6pt}

% ── List style ───────────────────────────────────────────────────────────────
\setlist[itemize]{
  leftmargin=1.2em,
  itemsep=1pt,
  parsep=0pt,
  topsep=2pt,
  label={\textcolor{navyblue}{\textbullet}}
}

% ── Entry command: Title \hfill Meta ────────────────────────────────────────
\newcommand{\entryhead}[2]{%
  \noindent\textbf{#1}\hfill{\small\textit{\textcolor{darkgray}{#2}}}\\[-4pt]%
}

\newcommand{\entrysub}[1]{%
  {\small\textit{\textcolor{darkgray}{#1}}}\\[2pt]%
}

% ── Bold inline label ────────────────────────────────────────────────────────
\newcommand{\blabel}[1]{\textbf{#1}\ }

% ═══════════════════════════════════════════════════════════════════════════
\begin{document}
% ═══════════════════════════════════════════════════════════════════════════

% ── HEADER ──────────────────────────────────────────────────────────────────
{\LARGE\bfseries\color{navyblue} NJOME DAVID}\\[4pt]
{\small\textcolor{darkgray}{%
  Melen, Yaoundé\quad|\quad
  \href{mailto:njomedavid26@gmail.com}{njomedavid26@gmail.com}\quad|\quad
  +237 671 711 462\quad|\quad
  \href{https://www.linkedin.com/in/njome-david-002a11213}{linkedin.com/in/njome-david-002a11213}\quad|\quad
  \href{https://github.com/Njome-David}{github.com/Njome-David}
}}

\vspace{4pt}
\textcolor{navyblue}{\rule{\linewidth}{1.8pt}}
\vspace{2pt}

% ── PERSONAL PROFILE ────────────────────────────────────────────────────────
\section{Personal Profile}

Third-year Computer Engineering student with hands-on experience across full-stack development,
databases, and networking, seeking an internship where I can apply and deepen my technical skills
in a demanding, real-world environment.

% ── EDUCATION ───────────────────────────────────────────────────────────────
\section{Education}

\entryhead{National Advanced School of Engineering Yaoundé — Computer Engineering}{09/2023 -- Present}
\entrysub{Yaoundé, Cameroon}
\begin{itemize}
  \item \blabel{Grade:} Very Good
  \item \blabel{Algorithmic:} Studied core data structures (trees, graphs, hash tables) and
        algorithms including sorting, searching, and dynamic programming. Developed analytical
        skills through complexity analysis (Big~O) to design optimised computational solutions.
  \item \blabel{Information Systems Conception:} Modelled structured, scalable information systems
        using Merise (MCD/MLD) and UML diagrams. Applied database design principles including
        normalisation to produce well-architected relational schemas ready for implementation.
\end{itemize}

\vspace{4pt}
\entryhead{Laval Bilingual College — General Secondary Education}{09/2016 -- 07/2023}
\entrysub{Douala, Cameroon}
\begin{itemize}
  \item Ranked \textbf{8th nationwide} at the GCE A-Level —
        Maths~A*, Physics~A*, ICT~A*, Further Maths~A*, Chemistry~A*
\end{itemize}

% ── PROJECTS ────────────────────────────────────────────────────────────────
\section{University / Personal Projects}

\entryhead{CROSS Authentication App \normalfont\small— Group Project (Leader)}{2025}
\begin{itemize}
  \item Platform enabling authorities to authenticate official documents using the CROSS Signature
        Scheme (Post-Quantum Cryptography).
  \item \blabel{Skills applied:} Project Management, Technical Documentation, Python.
  \item Led a team of 6 to design and deliver a fully functional post-quantum authentication
        platform within a 7-week timeline.
\end{itemize}

\vspace{4pt}
\entryhead{Illustrative Printing Room \normalfont\small- Individual Project}{2025}
\begin{itemize}
  \item OS-level simulation of a shared printing room where concurrent users with varying
        priorities, page counts, and print types compete for limited printers — demonstrating
        concurrency and synchronisation principles.
  \item \blabel{Skills applied:} Concurrency \& synchronisation, scheduling algorithm design,
        performance analysis, C~programming.
  \item Designed and benchmarked an original priority scheduling algorithm against FIFO and SJF
        across average waiting time, turnaround time, and starvation rate — achieving measurably
        better fairness outcomes.
\end{itemize}

% ── SKILLS ──────────────────────────────────────────────────────────────────
\section{Skills}

\vspace{2pt}
\noindent
\begin{tabularx}{\linewidth}{@{} >{\bfseries}p{4.8cm} X @{}}
  Programming
    & Python, Java, C/C++, HTML/CSS, JavaScript, GitHub, \LaTeX \\[3pt]
  Full-Stack Development
    & Next.js, React, Laravel, Spring Boot, PostgreSQL, MySQL \\[3pt]
  System Design \& Modelling
    & Merise, UML, database normalisation, requirements analysis \\[3pt]
  Leadership \& Project Management
    & Team coordination, sprint delivery, repeated group leadership \\[3pt]
  Mathematical Reasoning
    & Complexity analysis, discrete mathematics, algorithm design \\[3pt]
  Communication
    & Technical documentation, public speaking, cross-functional reporting \\
\end{tabularx}

% ── LANGUAGES ────────────────────────────────────────────────────────────────
\section{Languages}

\vspace{2pt}
\noindent
\begin{tabularx}{\linewidth}{@{} >{\bfseries}p{4.8cm} X @{}}
  French   & Fluent \\[3pt]
  English  & Fluent \\[3pt]
  Spanish  & Notions \\[3pt]
  German   & Notions \\
\end{tabularx}

% ── CERTIFICATIONS & AWARDS ──────────────────────────────────────────────────
\section{Certifications \& Awards}

\begin{itemize}
  \item Earned national certification in
        \textbf{Microsoft Excel 2016}, placing \textbf{1st in Cameroon} and
        qualifying to represent Cameroon at the World Skills Championship (2021 \& 2022).
  \item \textbf{Object Oriented Programming in Java} — IBM / Coursera \hfill \textit{\small\textcolor{darkgray}{Apr.\ 2026}}
  \item \textbf{Introduction to Object-Oriented Programming (in Java)} — EPFL / Coursera \hfill \textit{\small\textcolor{darkgray}{Apr.\ 2026}}
  \item \textbf{MAPLE Seminar} — NASEY OPTICA Chapter (Optica / OSA), ENSPY:\\
        \textit{2\textsuperscript{nd} Edition} (Feb.--Apr. 2025): awarded \textbf{Best Student Prize},
        ranking 1\textsuperscript{st} in the summative evaluation.\\
        \textit{3\textsuperscript{rd} Edition} (Feb.--Apr. 2026): returned as
        \textbf{Assistant Trainer \& Organizer}.
\end{itemize}

% ── EXTRACURRICULAR ACTIVITIES ───────────────────────────────────────────────
\section{Extracurricular Activities}

\begin{itemize}
  \item Served as \textbf{Junior Deputy of Cameroon to the United Nations}, representing national
        youth through diplomatic engagements, public speaking, interviews with political figures,
        and structured debates on the SDGs and broader UN development goals.
  \item Active member of the \textbf{GI Club ENSPY} project cell, contributing to collaborative
        engineering initiatives within the Computer Engineering department.
  \item Basketball player and team-based gaming enthusiast — strong appreciation for
        strategy, collaboration, and competition.
\end{itemize}

% ── REFERENCES ──────────────────────────────────────────────────────────────
\section{References}

\textit{\textcolor{darkgray}{Available upon request.}}

\end{document}
